\textbf{A Serious Game for Aiding the Screening of Dyslexia in Children and Young Adults}

### 2014-06-15 acticle.tex
Add Issue Categories
Add Working Memory

>>>>

\subsubsection{Working Memory}
\label{sec:memory}
Individuals with dyslexia often struggle to remember list items, sequences, and even the contents of text they have just read \cite{snowling}. The reasons for this from a scientific perspective are debated, however, from a high level it seems that someone with dyslexia will put a large amount of effort into interpreting and reading the words, concentrating on understanding them as opposed to remembering them \cite{neurobiological}.
\cite{snowling} states that: ``Dyslexics typically perform poorly when their memory is assessed using tests such as the digit span task, in which sequences of digits have to be recalled in forwards and backwards order"
This suggests that the auditory memory of an individual with dyslexia can be impaired by the learning disorder, this effect was also seen by \cite{memory1980} when conducting a similar experiment.

\subsubsection{Spatial Orientation}

\subsubsection{Visual-spatial Discrimination}

\subsubsection{Visual Sequential Memory}

\subsubsection{Visual Memory}
